The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-06 paper/main.tex
Started on the abstract.

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}

@@

\begin{abstract}
my abstract
\end{abstract}

\noindent \textbf{Keywords.} list of keywords

@@

\emph{Hypothesis 3: There will be more Issue Reporters than Committers by an order of magnitude, but the number of Committers will remain small.}\\
Research into the Apache Server project observed that there were far more \emph{Issue Reporters} than there were code \emph{Committers}\cite{mockus2000case}. The Apache Server project is an excellent case study in this type of Developer Hierarchy. Apache is built around a small set of {\it Core Developers}, followed by {\it Defect Repairers} and {\it Defect Reporters}. Each level of this hierarchy brings with it an order of magnitude increase in number of participants. The 10-15 {\it Core Developers} contribute around 80\% of the new functionality, while the rest of the 400 code contributors focus primarily on bug fixes. The {\it Defect Reporters} were by far the largest group, with over 3000 individuals submitting bug reports.\\

@@

\emph{Research Question 1: There will be more Issue Reporters than Committers by an order of magnitude, but the number of Committers will remain small.}\\
A smal core of developers, however, seems to be a historial fact of OSS development\cite{mockus2000case,mockus2000two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changes this?

@@

@@

\section{Results}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}

@@

\subsection{Other Findings}
\emph{The Git SCM }\\

\emph{The GitHub Process applies to more than code artifacts}\\

>>>>

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}
\setlength\parindent{0pt}

@@

\begin{abstract}
Open Source Software (OSS) has produced many successful projects. The development process by which these projects are produced is generally unstructured compared to commercial software -- but a definite pattern does arrive, and is no less a pattern. GitHub, a popular OSS code hosting website, and Git, the site's SCM of choice, may have the potential to fundamentally change ths process.\\
By analyzing a subset of GitHub repositories, this report will show how GitHub has influenced some very intrinsic aspects of traditional OSS develoment, such as developer hierarchies and issue close velicity. We find that... TODO
\end{abstract}

\noindent \textbf{Keywords.} Git, GitHub, OpenSource

@@

\emph{Hypothesis 3: There will be more Issue Reporters than Committers by an order of magnitude}\\
Research into the Apache Server project observed that there were far more \emph{Issue Reporters} than there were code \emph{Committers}\cite{mockus2000case}. The Apache Server project is an excellent case study in this type of Developer Hierarchy. Apache is built around a small set of {\it Core Developers}, followed by {\it Defect Repairers} and {\it Defect Reporters}. Each level of this hierarchy brings with it an order of magnitude increase in number of participants. The 10-15 {\it Core Developers} contribute around 80\% of the new functionality, while the rest of the 400 code contributors focus primarily on bug fixes. The {\it Defect Reporters} were by far the largest group, with over 3000 individuals submitting bug reports.\\

@@

\emph{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
A smal core of developers, however, seems to be a historial fact of OSS development\cite{mockus2000case,mockus2000two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changes this?

@@

\emph{Research Question 3: Can GitHub be used for more that code artifacts?}\\
The Object Managment Group\textregistered\footnote{http://www.omg.org} computer industry consortium focused on technology standards. Potential standard summission teams must go through a vetting process\cite{kobryn1999uml} which allows industry representatives to provide feedback on the standard. Gathering and recording this feedback is a challenge, but GitHub's issue tracking system may be able to streamline the process.

@@

\section{Results}
\subsection{Hypotheses}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}

@@

\subsection{Research Questions}
\emph{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\

\emph{Research Question 2: What is the GitHub Philosophy?}\\

\emph{Research Question 3: Can GitHub be used for more that code artifacts?}\\
